01_Vegetation_cover

### 2022-11-10 01_Species_abundance.Rmd
fix joining issue

# join df's from both zones
canop <- canop_b %>% 
  left_join(canop_c, by = c("sitename","species"))
```

>>>>

# join df's from both zones
canop <- canop_b %>% 
  full_join(canop_c, by = c("sitename", "species")) %>% 
  filter(!(is.na(spec_abun_b) & is.na(spec_abun_c))) %>% 
  replace_na(list(spec_abun_b = 0,
                  spec_abun_c = 0))
```
